An Empirical Analysis of the Role of Energy in Economic Growth

### 2014-05-04 Article/EconGrowth2.Rnw
Converting EconGrowth2.Rnw to use the new AllCoef.rda and AllFitted.rda files.

<<setup, echo=FALSE, message=FALSE, eval=TRUE>>=
require(EconModels)
require(EconData)
require(lattice)
require(latticeExtra)
require(ggplot2)
require(car)
require(mosaic)
require(xtable)
require(nlmrt)
require(micEconCES)
require(plyr)
# Provides access to data melting. 
# See http://cran.r-project.org/web/packages/reshape2/reshape2.pdf
require(reshape2) 
# tikz allows use of LaTeX formatting and font in graphs. 
# Allows for a consistent look across the paper.
# See http://r-forge.r-project.org/R/?group_id=440 for instructions 
# on installing tikzDevice.
# require(tikzDevice) 
trellis.par.set(theme=theme.mosaic())
options(width=75)
options(show.signif.stars=TRUE)
require(knitr)

# Pull in some constants and other important functions
#source("Scripts/files.R")
#source(file.path("..", "Scripts", "Constants.R"))

# Load historical data
# In Rstudio, this paper is generated from it's directory, which is "Article".
# We need to define paths relative to the location of the paper. 
# Relative path to historical data from Article
# baseHistorical <- file.path("..", "data")
historicalData <- Econ2011 # From the EconData package

# Set up for loading resample results
# We need to define a directory path from "Article" to the resample data results
archive <- file.path("..", "data_resample_2014-05-02_Refactored-EconData_n=1000.zip")
# baseResample <- "data_resample" # Define the directory within the archive wherein we can find the data.
# Load the fits to the original historical data out of the archive we're using.
# This object (oModels) should be passed in to functions that need information from orig fits.
f <- gzcon(unz(description=archive, filename=file.path("oModels.Rdata")))
oModels <- readRDS(f)
close(f)

opts_chunk$set(
  # ********************************************************
  eval=FALSE,
  # ********************************************************
  # tikz allows LaTeX code in graphical output. 
  # E.g., "$y$" for a variable name in the legend for a graph.  
  # dev='tikz',
  tidy=FALSE,
  comment=NA,
  # Tells whether to cache output from chunks are saved. Cacheing saves time. 
  # However, references to LaTeX tables DO NOT WORK if cacheing is turned on.
  cache=FALSE,
  warning=FALSE,  #Tells whether to show warnings in the output.
  # Turns off messages for all chunks. 
  # Set TRUE on an individual chunk to see it.
  message=FALSE, 
  # Tells whether to echo code for all chunks. 
  # Set TRUE on an individual chunk to see its code.
  echo=FALSE     
)
@

@@

\twocolumn{}
<<CD_Ternary_Scatter_Graph, fig.pos="H", fig.align='center', fig.width=2.9, fig.height=7.7, fig.cap="Cobb-Douglas resample model parameters.">>=
cdCoeffsData <- loadResampledData(archive=archive, 
                                  country=countryAbbrevs, 
                                  model="cd", 
                                  factors=c("iK+iL", "iK+iL+iQ"), 
                                  kind="coeffs")
# Rearrange the country factors to obtain our preferred ordering.
cdCoeffsData$country <- as.factor(cdCoeffsData$country)
for (lev in rev(countryAbbrevs)) { cdCoeffsData$country <- relevel(cdCoeffsData$country, ref=lev) }
# Rearrange the energy factors to obtain our preferred ordering.
cdCoeffsData$energy <- replace(cdCoeffsData$energy, which(is.na(cdCoeffsData$energy)), "none")
cdCoeffsData$energy <- as.factor(cdCoeffsData$energy)
energyLevels <- c(none="none", Q="iQ")
for (lev in rev(energyLevels)) { cdCoeffsData$energy <- relevel(cdCoeffsData$energy, ref=lev) }
standardTriPlot(data=cdCoeffsData, facet_formula=country~energy)
@

<<CD_GDP_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=3, fig.height=8.2, fig.cap="Cobb-Douglas fitted models.">>=
# cdData <- loadCDSpaghettiGraphData(energyType="none", baseHistorical=baseHistorical, baseResample=baseResample)
# cdQData <- loadCDSpaghettiGraphData(energyType="Q", baseHistorical=baseHistorical, baseResample=baseResample)
# cdData <- rbind(cdData, cdQData)
cdFittedData <- loadResampledData(archive=archive, 
                                  country=countryAbbrevs, 
                                  model="cd", 
                                  factors=c("iK+iL", "iK+iL+iQ"), 
                                  kind="fitted")
spaghettiPlot(data=cdSpagData, facet_formula=Country~Energy, level=spaghettiGraphLevel) +
    labs(y="Indexed GDP (1980=1 or 1991=1)")
@
\onecolumn{}

@@

<<CES_lambda_gamma_graph, fig.pos="H", fig.align='center', fig.width=fourPanelScatterGraphWidth, fig.height=ninePanelScatterGraphHeight, fig.cap="$\\lambda$ and $\\gamma$ values for CES resample models.">>=
cesCoeffsData <- loadResampledData(archive=archive, 
                                   country=countryAbbrevs, 
                                   model="ces", 
                                   factors=c("iK+iL", "iK+iL+iQ", "iL+iQ+iK", "iQ+iK+iL"), 
                                   kind="coeffs")
# Rearrange the country factors to obtain our preferred ordering.
cesCoeffsData$country <- as.factor(cesCoeffsData$country)
for (lev in rev(countryAbbrevs)) { cesCoeffsData$country <- relevel(cesCoeffsData$country, ref=lev) }
standardScatterPlot(data=cesCoeffsData, mapping=aes(gamma_coef, lambda), facet_formula=country~nestStr, alpha=0.05) +
    scale_x_continuous(breaks=c(0.9, 1.0, 1.1)) +
    scale_y_continuous(breaks=c(0, 0.025, 0.05, 0.075)) +    
    labs(x=expression(gamma), y=expression(lambda))
@

<<CES_sigma1_delta1_graph, fig.pos="H", fig.align='center', fig.width=fourPanelScatterGraphWidth, fig.height=ninePanelScatterGraphHeight, fig.cap="$\\sigma_1$ and $\\delta_1$ values for CES resample models.">>=
standardScatterPlot(data=cesCoeffsData, mapping=aes(delta_1, sigma_1), facet_formula=country~nestStr, alpha=0.05) +
    coord_trans(y="sigma") +
    scale_x_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
    scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
    labs(x=expression(delta[1]), y=expression(sigma[1]))
@

<<CES_sigma_delta_graph, fig.pos="H", fig.align='center', fig.width=4.5, fig.height=7, fig.cap="$\\sigma$ and $\\delta$ values for CES resample models.">>=
standardScatterPlot(data=subset(cesCoeffsData, nestStr != "iK+iL"),
                    mapping=aes(delta, sigma), facet_formula=country~nestStr, alpha=0.05) +
    coord_trans(y="sigma") +
    scale_x_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
    scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
    labs(x=expression(delta), y=expression(sigma))
@

@@

<<CES_ternary_graph, fig.pos="H", fig.align='center', fig.width=5.5, fig.height=7.5, fig.cap="$\\alpha$, $\\beta$, and $\\gamma$ values for CES resample models.">>=
# cesTriPlotData=loadCESResampleData(energyType="Q", nest="all", baseResample=baseResample)
# standardTriPlot(data=cesTriPlotData)
standardTriPlot(data=cesCoeffsData, facet_formula=country~nestStr)
@

@@

<<CES_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=8.5, fig.cap="CES fitted models.">>=
cesFittedData <- loadResampledData(archive=archive, 
                                   country=countryAbbrevs, 
                                   model="ces",
                                   factors=c("iK+iL", "iK+iL+iQ", "iL+iQ+iK", "iQ+iK+iL"), 
                                   kind="fitted")
spaghettiPlot(data=cesFittedData, facet_formula=Country~nestStr, level=spaghettiGraphLevel) +
    labs(y="Indexed GDP (1980=1 or 1991=1)")
@

>>>>

<<setup, echo=FALSE, message=FALSE, eval=TRUE>>=
require(EconModels)
require(EconData)
require(lattice)
require(latticeExtra)
require(ggplot2)
require(car)
require(mosaic)
require(xtable)
require(nlmrt)
require(micEconCES)
require(plyr)
require(dplyr)
# Provides access to data melting. 
# See http://cran.r-project.org/web/packages/reshape2/reshape2.pdf
require(reshape2) 
# tikz allows use of LaTeX formatting and font in graphs. 
# Allows for a consistent look across the paper.
# See http://r-forge.r-project.org/R/?group_id=440 for instructions 
# on installing tikzDevice.
# require(tikzDevice) 
trellis.par.set(theme=theme.mosaic())
options(width=75)
options(show.signif.stars=TRUE)
require(knitr)

# Load historical data
# In Rstudio, this paper is generated from it's directory, which is "Article".
# We need to define paths relative to the location of the paper. 
# Relative path to historical data from Article
historicalData <- Econ2011 # From the EconData package

# Load coefficients from all models in one large data frame
coef_df<- tbl_df( readRDS("../AllCoef.rda") )
fitted_df <- tbl_df( readRDS("../AllFitted.rda") )

# Set up for loading resample results
# We need to define a directory path from "Article" to the resample data results
# archive <- file.path("..", "data_resample_2014-05-02_Refactored-EconData_n=1000.zip")
# baseResample <- "data_resample" # Define the directory within the archive wherein we can find the data.
# Load the fits to the original historical data out of the archive we're using.

# Load the original models.
# f <- gzcon(unz(description=archive, filename=file.path("../oModels.Rdata")))
oModels <- readRDS(file=file.path("..", "oModels.Rdata"))
close(f)

opts_chunk$set(
  # ********************************************************
  eval=TRUE,
  # ********************************************************
  # tikz allows LaTeX code in graphical output. 
  # E.g., "$y$" for a variable name in the legend for a graph.  
  # dev='tikz',
  tidy=FALSE,
  comment=NA,
  # Tells whether to cache output from chunks are saved. Cacheing saves time. 
  # However, references to LaTeX tables DO NOT WORK if cacheing is turned on.
  cache=FALSE,
  warning=FALSE,  #Tells whether to show warnings in the output.
  # Turns off messages for all chunks. 
  # Set TRUE on an individual chunk to see it.
  message=FALSE, 
  # Tells whether to echo code for all chunks. 
  # Set TRUE on an individual chunk to see its code.
  echo=FALSE     
)
@

@@

\twocolumn{}
<<CD_Ternary_Scatter_Graph, fig.pos="H", fig.align='center', fig.width=2.9, fig.height=7.7, fig.cap="Cobb-Douglas resample model parameters.">>=
cdCoeffsData <- filter(coef_df, model=="cd", nestStr==c("iK+iL", "iK+iL+iQ"))

# Rearrange the country factors to obtain our preferred ordering.
cdCoeffsData$country <- as.factor(cdCoeffsData$country)
for (lev in rev(countryAbbrevs)) { cdCoeffsData$country <- relevel(cdCoeffsData$country, ref=lev) }
# Rearrange the energy factors to obtain our preferred ordering.
cdCoeffsData$energy <- replace(cdCoeffsData$energy, which(is.na(cdCoeffsData$energy)), "none")
cdCoeffsData$energy <- replace(cdCoeffsData$energy, which(cdCoeffsData$energy=="iQ"), "q")
cdCoeffsData$energy <- as.factor(cdCoeffsData$energy)
energyLevels <- c(none="none", q="q")
for (lev in rev(energyLevels)) { cdCoeffsData$energy <- relevel(cdCoeffsData$energy, ref=lev) }
standardTriPlot(data=cdCoeffsData, facet_formula=country~energy)
@

<<CD_GDP_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=3, fig.height=8.2, fig.cap="Cobb-Douglas fitted models.">>=
cdFittedData <- filter(fitted_df, model=="cd", nest==c("iK+iL", "iK+iL+iQ"))
# Rearrange the energy factors to obtain our preferred ordering.
cdFittedData$energy <- replace(cdFittedData$energy, which(is.na(cdFittedData$energy)), "none")
cdFittedData$energy <- replace(cdFittedData$energy, which(cdFittedData$energy=="iQ"), "q")
cdFittedData$energy <- as.factor(cdFittedData$energy)
energyLevels <- c(none="none", q="q")
for (lev in rev(energyLevels)) { cdFittedData$energy <- relevel(cdFittedData$energy, ref=lev) }
spaghettiPlot(data=cdFittedData, facet_formula=Country~energy, level=spaghettiGraphLevel) +
    labs(y="Indexed GDP (1980=1 or 1991=1)")
@
\onecolumn{}

@@

<<CES_lambda_gamma_graph, fig.pos="H", fig.align='center', fig.width=fourPanelScatterGraphWidth, fig.height=ninePanelScatterGraphHeight, fig.cap="$\\lambda$ and $\\gamma$ values for CES resample models.">>=
cesCoeffsData <- filter(coef_df, model=="ces", nestStr==c("iK+iL", "iK+iL+iQ", "iL+iQ+iK", "iQ+iK+iL"))
# Rearrange the country factors to obtain our preferred ordering.
cesCoeffsData$country <- as.factor(cesCoeffsData$country)
for (lev in rev(countryAbbrevs)) { cesCoeffsData$country <- relevel(cesCoeffsData$country, ref=lev) }
standardScatterPlot(data=cesCoeffsData, mapping=aes(gamma_coef, lambda), facet_formula=country~nest, alpha=0.05) +
    scale_x_continuous(breaks=c(0.9, 1.0, 1.1)) +
    scale_y_continuous(breaks=c(0, 0.025, 0.05, 0.075)) +    
    labs(x=expression(gamma), y=expression(lambda))
@

<<CES_sigma1_delta1_graph, fig.pos="H", fig.align='center', fig.width=fourPanelScatterGraphWidth, fig.height=ninePanelScatterGraphHeight, fig.cap="$\\sigma_1$ and $\\delta_1$ values for CES resample models.">>=
standardScatterPlot(data=cesCoeffsData, mapping=aes(delta_1, sigma_1), facet_formula=country~nest, alpha=0.05) +
    coord_trans(y="sigma") +
    scale_x_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
    scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
    labs(x=expression(delta[1]), y=expression(sigma[1]))
@

<<CES_sigma_delta_graph, fig.pos="H", fig.align='center', fig.width=4.5, fig.height=7, fig.cap="$\\sigma$ and $\\delta$ values for CES resample models.">>=
standardScatterPlot(data=subset(cesCoeffsData, nestStr != "iK+iL"),
                    mapping=aes(delta, sigma), facet_formula=country~nest, alpha=0.05) +
    coord_trans(y="sigma") +
    scale_x_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
    scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
    labs(x=expression(delta), y=expression(sigma))
@

@@

<<CES_ternary_graph, fig.pos="H", fig.align='center', fig.width=5.5, fig.height=7.5, fig.cap="$\\alpha$, $\\beta$, and $\\gamma$ values for CES resample models.">>=
# cesTriPlotData=loadCESResampleData(energyType="Q", nest="all", baseResample=baseResample)
# standardTriPlot(data=cesTriPlotData)
standardTriPlot(data=cesCoeffsData, facet_formula=country~nest)
@

@@

<<CES_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=8.5, fig.cap="CES fitted models.">>=
cesFittedData <- filter(fitted_df, model=="ces", nest==c("iK+iL", "iK+iL+iQ", "iL+iQ+iK", "iQ+iK+iL"))
spaghettiPlot(data=cesFittedData, facet_formula=Country~nest, level=spaghettiGraphLevel) +
    labs(y="Indexed GDP (1980=1 or 1991=1)")
@
